IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-23 response.tex

		\begin{point}
			The time complexity of the proposed algorithms, especially involving branch and bound methods, seems to be high especially applications assuming perfectly CSI availability as the coherence times are practically pretty low. So, the authors would like to justify it so that the proposed solution can be obtained over relatively short coherence intervals.
			\label{pt:2.7}
		\end{point}

		\begin{response}
			Problem \eqref{M-op:irs} is not a Semidefinite Programming (SDP) due to the squared term in the objective function. Hence, existing complexity analysis tools cannot be direct applied to Algorithm~\ref{M-al:sca} and \ref{M-al:m_sca}. For Algorithm~\ref{M-al:gp}, the computational complexity scales exponentially with the number of subbands \cite{M-Huang2017,M-Chiang2005} but an analytical expression cannot be derived on top of relevant literatures. To facilitate practical SWIPT implementation and address the reviewer's comment, we have added in the revised manuscript two closed-form adaptive waveform amplitude design by combining WF and SMF under TS and PS setups. The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{M-Tse2005} and the details are omitted here. On the other hand, SMF was proposed in \cite{M-Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session. In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}

			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes. To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized. To achievable non-WIT points, the rate constraint \eqref{M-co:irs_rate} should be dropped as the R-E region is now characterized by varying either $\eta$ or $\delta$ and $\rho$. Algorithm~\ref{M-al:m_sca} summarizes the modified passive beamforming design for low-complexity PS mode. The tightness of rank relaxation and local optimality can be proved similar to Proposition~\ref{M-pr:relaxation} and \ref{M-pr:sca}, and the details are omitted here. Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations.

@@

			\begin{figure}[!h]
				\centering
				\subfloat[Average noise power\label{fi:re_noise}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_noise.tex}
					}
				}
				\subfloat[AP-IRS horizontal distance\label{fi:re_distance}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_distance.tex}
					}
				}
				\\
				\subfloat[Transmit antennas\label{fi:re_tx}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_tx.tex}
					}
				}
				\subfloat[Reflecting elements\label{fi:re_reflector}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_reflector.tex}
					}
				}
				\caption{Average achievable R-E region under different configurations.}
			\end{figure}
			\label{re:2.7}
		\end{response}

		\begin{point}
			How practical is it to consider lossless reflection from the RIS? Specifically, by considering the magnitude to be 1, the reflection losses at the RIS have been ignored.
			\label{pt:2.8}
		\end{point}

		\begin{response}
			The assumption of lossless reflection is indeed ideal but common in microwave theory (e.g., \cite{Shen2020a}). Based on the circuit analysis, the authors of \cite{M-Abeywickrama2019} shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance. For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} for $\theta_l=\pi$ but around \num{0.6} for $\theta_l=\num{0}$. From the perspective of field and propagation, \cite{Ozdogan2020} points out that if the dimension of IRS element is much larger than the wavelength, the beamwidth would become small and the scattered field strength would depend on the observation angle. However, to reduce the design complexity and provide a preliminary insight, we considered the lossless reflection pattern at the IRS in this paper.
			\label{re:2.8}
		\end{response}

@@

			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm that obtains the IRS phase shift by a relax-then-extract method, where the performance loss by rank relaxation is proved negligible. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the waveform and splitting ratios for PS. The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.

			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to multi-carrier energy transfer, especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) to achieve different R-E tradeoff, the active and passive beamforming can be fixed for narrowband SWIPT but need adaptive design for broadband SWIPT, 7) the proposed algorithms are robust to practical restrictions as inaccurate cascaded CSIT and finite IRS reflection states.
			\label{re:3.2}
		\end{response}

@@

		\begin{point}
			Please explain the derived results more intuitively for better understanding.
			\label{pt:3.3}
		\end{point}

		\begin{response}
			We have updated the discussion carefully and the reviewer is referred to the updated manuscript.
			\label{re:3.3}
		\end{response}

		\begin{point}
			Authors assumed the unrealistic situation: the channels are assumed to be perfectly known. However, in practice, the channel should be estimated, e.g., as studied in \cite{You2019,Kang2020}. It would be much better to discuss the channel estimation issue by citing the above references.
			\label{pt:3.4}
		\end{point}

		\begin{response}
			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance. The reviewer is referred to Response \ref{re:1.1} for details. Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed joint waveform, active and passive beamforming algorithm to cascaded CSIT inaccuracy with different number of IRS elements.
			\label{re:3.4}
		\end{response}

@@

		\begin{point}
			More simulation results should be added to better and aggregately validate the effectiveness of the proposed method.
			\label{pt:3.5}
		\end{point}

		\begin{response}
			Thank you for the suggestion. On top of the previous version, we have introduced two closed-form adaptive waveform design under TS and PS modes and compared the results with the original BCD Algorithm~\ref{M-al:bcd}. Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{M-al:lc_bcd} achieves near-optimal performance under different configurations. Moreover, we have investigated in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization} the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region. It can be concluded that the proposed algorithms are robust to CSIT inaccuracy of the cascaded link, and even $b=1$ (i.e. two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS. These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
